### 2024-10-04 MSc.tex
Updated tables in 5 and added 6
Updated abstract

\setkomafont{section}{\huge} % The title "Abstract" and "Útfdráttur" should look like the chapters, i.e. use \huge (\chapter cannot be used as this would create a new page)
\section*{Abstract}
English abstract (ca. 250 words).

\vfill \vspace*{1cm}

\section*{Útdráttur}
Hér kemur útdráttur á íslensku sem er að hámarki 250 orð.
\vfill

@@

\include{Chapters/Chapter1}
\include{Chapters/Chapter2}
\include{Chapters/Chapter3}
\include{Chapters/Chapter4}
\include{Chapters/Chapter5}

>>>>

\setkomafont{section}{\huge} % The title "Abstract" and "Útfdráttur" should look like the chapters, i.e. use \huge (\chapter cannot be used as this would create a new page)
\section*{Abstract}
In many industries, whether it be windmill farming or transportation, being able to precisely predict the load caused by weather is crucial to prevent harm coming to people and machinery as well as increasing productivity. The efficiency of wind turbines in low wind speed conditions is a critical challenge in optimizing renewable energy systems. Gust predictions can be instrumental in loss prevention. If looking only at wind, the most destructive moments are gusts, by definition. To predict these values there are two ways, traditional numerical weather prediction systems and machine learning or other pattern recognition systems. Computer aided numerical weather prediction systems originated in the 1950's, while the use of machine learning in numerical weather predictions is much more recent, having truly gained traction in the last decade.

The goal of this thesis is try to combine these two methods to try and predict wind gust factor, where the gust factor is defined as the ratio between wind gust and average wind speed. This is done by having the input data to the machine learning model be reanalysis variables that were generated by traditional numerical weather prediction systems. In addition to these variables and derived variables, a digital elevation model (DEM) data was used. A deep neural network was constructed using some set of variables and the results are compared to a baseline as well as each other so as to show the impact each feature has.
\vfill \vspace*{1cm}

\section*{Útdráttur}
Í mörgum iðnuðum, hvort sem það er vindmyllubúgarður eða flutningar, að geta 
\vfill

@@

\include{Chapters/Chapter1}
\include{Chapters/Chapter2}
\include{Chapters/Chapter3}
\include{Chapters/Chapter4}
\include{Chapters/Chapter5}
\include{Chapters/Chapter6}
